
\noindent
\obeylines

\definecolor{myblue}{RGB}{230,240,250}
\pagecolor{myblue}

\subsection*{Myocardial Infarction and CAD Form}
\setcounter{counter}{0}
\label{Hospitalization Form}
\label{Heart attack or myocardial infarction}

You answered that you had a \textbf{heart attack (myocardial infarction), chest pain, angina, or coronary artery disease} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 

% \ConditionHospitalizationOnly
\ConditionHospitalizationOnlySpecific{heart attack (myocardial infarction), chest pain, angina, or coronary artery disease}

% \subsection*{CAD Form}
% \setcounter{counter}{0}
% \label{CAD}

% You answered that you had \textbf{chest pain, coronary artery disease, or angina} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 

% % \ConditionHospitalizationOnly
% \ConditionHospitalizationOnlySpecific{coronary artery disease (CAD) or angina}

\newpage

\subsection*{Heart Failure Form}
\setcounter{counter}{0}
\label{Heart failure}

You answered that you had \textbf{heart failure} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 


% \OutpatientOrHospitalization{diagnosis}{condition}
\OutpatientOrHospitalizationSpecific{diagnosis}{heart failure}{}

\newpage

\subsection*{Atrial Fibrillation Form}
\setcounter{counter}{0}
\label{Atrial fibrillation}

You answered that you had \textbf{atrial fibrillation or atrial flutter} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 


% \OutpatientOrHospitalization{diagnosis}{condition}
\OutpatientOrHospitalizationSpecific{diagnosis}{atrial fibrillation or atrial flutter}{}

\newpage

\subsection*{Stroke Form}
\setcounter{counter}{0}
\label{Stroke}

You answered that you had a \textbf{stroke} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 

% \ConditionHospitalizationOnly
\ConditionHospitalizationOnlySpecific{stroke}

\subsection*{TIA Form}
\setcounter{counter}{0}
\label{Transient Ischemic Attack}

You answered that you had a \textbf{mini-stroke or transient ischemic attack (TIA)} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 

% \ConditionHospitalizationOnly
\ConditionHospitalizationOnlySpecific{mini-stroke or transient ischemic attack (TIA)}

\newpage

\subsection*{PE/DVT Procedure Form}
\setcounter{counter}{0}
\label{Pulmonary embolism/DVT}

You answered that you had a \textbf{blood clot in your leg or lung requiring blood thinning medicine (pulmonary embolism [PE]/deep vein thrombosis [DVT])} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 

\setcounter{counter}{0}

 %blood clot in leg vein or lung
\vcounterlist\item \FetchText{HCP17.}
\vsublist
\item \FetchText{HCP17.1}
\item \FetchText{HCP17.2}
\item \FetchText{HCP17.3}
\item \FetchText{HCP17.4}\setc{-1}
% \item \FetchText{HCP17.5}
\vsublistend
\vlistend

\vcounterlist\item \FetchText{HCP17b.}
\YN


\OutpatientOrHospitalizationPulmonary{diagnosis}{pulmonary embolism (PE)/DVT (deep vein thrombosis)}
% \BloodFlowProcedure



\newpage

\subsection*{Heart Procedure Form}
\setcounter{counter}{0}
\label{Procedure to Increase Blood Flow to Heart}

You answered that you had a \textbf{procedure to increase blood flow to your heart (e.g., CABG, and stent)} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 
 
\BloodFlowProcedure

\newpage

\subsection*{Brain Procedure Form}
\setcounter{counter}{0}
\label{Procedure to Increase Blood Flow to Brain}

You answered that you had a \textbf{procedure to increase blood flow to your brain} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 
 
\BloodFlowProcedure

\newpage

\subsection*{Vascular Procedure Form}
\setcounter{counter}{0}
\label{Procedure to Increase Blood Flow to Legs}

You answered that you had a \textbf{procedure to increase blood flow to the legs} since the date of your in-person MOSAAIC exam. We have some follow-up questions. 

\BloodFlowProcedure

\newpage

\subsection*{Additional Hospitalizations Form}
\label{Additional Hospitalizations}

\newcommand{\AdditionalHospitalizationBox}[1]{%
\begin{minipage}{.49\textwidth}
\begin{tcolorbox}[width = \textwidth, boxsep = 0pt]
\begin{center}{\textbf{Hospitalization #1:}}\end{center}\raggedright

\smallskip
\HospitalName[nocounter]
\HospitalLocation[nocounter]
\HospitalDateNoCounter
\MainCondition

\end{tcolorbox}%
\end{minipage}%
}

\AdditionalHospitalizationBox{1}%
\AdditionalHospitalizationBox{2}%

\AdditionalHospitalizationBox{3}%
\AdditionalHospitalizationBox{4}%
