\newcommand{\y}{\hspace*{.05 cm}\rule{.3 cm}{.25 mm}\hspace*{.05cm}} 
\renewcommand{\vlist}[1]{\raggedright\raggedbottom\begin{enumerate}[label =#1, start = 1, itemsep=.5em, topsep=.5em, left=0em, labelsep=.25em, align = left]}
\renewcommand{\hlist}[1]{\bmp\begin{enumerate}[label =#1]\raggedright\raggedbottom} %non-indented horizontal lists
\renewcommand{\vsublist}{\begin{enumerate}[left = 1em, start = 1, itemsep=.5em, topsep=.5em, left=0em, labelsep=.25em, align = left]}
\renewcommand{\hsublist}{\vspace{.75em}\begin{enumerate*}[label = \hspace{.4em}\arabox, labelsep=.25 em, start = 1, topsep=.75em, align = parleft, itemjoin=\hspace{1.1em}]}
\newcommand{\bmptwo}{\bmp
\setlength{\parskip}{7.25ptplus2.0pt}
\setlength{\itemsep}{6pt}
\setlength{\topsep}{6pt}
}
\newcommand{\emptwo}{\emp\vspace{.5em}
}
\renewcommand{\sectionbreak}{}
\renewcommand{\subsectionbreak}{}


\noindent
\obeylines

\markright{\ratch{SFT0.}}
\section{\touch{SFT0.}}

\vspace{-2\baselineskip}
\renewcommand{\arraystretch}{1.5}
\begin{longtable}{ @{} >{\rrr} p{.75 cm}  >{\rrr} p{11.85 cm}  >{\llslash} p{1 cm}  >{\ccc} p{1.5 cm}}
&&{\bf\makecell[b]{\punch{Yes}}} & {\bf\makecell[b]{\punch{No}}}\\
SAF1. & \fetch{SAF1.}\twobox
SAF2. & \fetch{SAF2.}\twobox 
SAF3. & \fetch{SAF3.}\twobox
SAF4. & \fetch{SAF4.}\twobox
SAF5. & \fetch{SAF6.}\twobox
SAF6. & \fetch{SAF10.}*\twobox
SAF7. & \fetch{SAF11.}*\twobox
\\\end{longtable}
\vspace{-2\baselineskip}
*If a participant checked either condition above, s/he will not be eligible for bronchodilator administration (post test), but can still be eligible for pre-spirometry test.
\begin{longtable}{ @{} >{\rrr} p{.3 cm} >{\rrr} p{.5 cm} @{} >{\rrr} p{12.0 cm}  >{\llslash} p{1 cm}  >{\ccc} p{1.5 cm}}
SAF8. && \fetch{SAF14.} &{\bf\makecell[t]{\punch{Yes}}} & {\bf\makecell[t]{\punch{No}}}\endfirsthead
% &a. & \fetch{SAF14.13}\twobox
&a. & \fetch{SAF14.1}\twobox
&b. & \fetch{SAF14.2}\twobox 
&c. & \fetch{SAF14.3}\twobox
&d. & \fetch{SAF14.4}*\twobox
&e. & \fetch{SAF14.5}**\twobox
&f. & \fetch{SAF14.6}**\twobox 
&g. & \fetch{SAF14.7}**\twobox
&h. & \fetch{SAF14.8}\twobox
&i. & \fetch{SAF14.14}**\twobox
&j. & \fetch{SAF14.9}\twobox
&k. & \fetch{SAF14.10}\twobox
&l. & \fetch{SAF14.11}\twobox
&m. & \fetch{SAF14.12}*\twobox\end{longtable}
\vspace{-1\baselineskip}
\begin{minipage}{\textwidth}
If a participant checked any condition listed above, s/he will not be eligible for spirometry testing. However, testing can be rescheduled for conditions marked with * or **, \textcolor{red}{if no other conditions marked:}
\begin{enumerate}[label = $\bullet$, left = 2em, align = left, itemsep = .1 em, topsep = .25em]
              \item[*] Pulmonary testing can be rescheduled for a date as early as one week later
              \item[**] Pulmonary testing can be rescheduled for a date as early as four weeks later
\end{enumerate}
\end{minipage}
% \vspace{-.75\baselineskip}
\bmp
\vlist{SAF9.}\item \fetch{SAF5.} 
\vsublist
\item \hatch{SAF5.1} %\hrulefill
\setc{-1}
\item \fetch{SAF5.2}
\end{enumerate}\end{enumerate}
\emp
\hlist{SAF10.}\item \fetch{SAF12.}

\hsublist
\item \fetch{SAF12.1}
\item \fetch{SAF12.2}
\pop

\vlist{SAF11.}\item \fetch{SAF13.}
\vsublist
\ice \triple{\x\x:\x\x}{SAF13.1}
\end{enumerate}
\end{enumerate}

\label{myLastPage}
